Flat-histogram method comparison on the 2D Ising model

### 2020-06-25 ising/ising-body.tex
edit of the discussion

% This goes in discussion section
Last time for 32 X 32 is TL 2047388. Do I look at histogram to figure this out??
But optimized ensemble requires the energy range???
Also, SAD doesn't appear to be impacted by the larger energy range? histogram counts outside the interesting energy range are negligible compared with count in the range of interest.

@@

>>>>

@@

Figure~\ref{fig:N128-cv-error} shows that the SAD algorithm converges
signiticantly more slowly that the converging WL methods.
%We interpret this as due to the
%fact that the SAD simulation must take the time to discover the energy range
%of interest dynamically.
The SAD algorithm on average takes around
\davidsays{$10^9$} moves to identify as important all \davidsays{8192}
negative energy states, which is around \davidsays{twice as long} as
the number of moves that
the WL methods require in order to explore all the states in this
energy range.  The main difference between the convergence of these
methods is that the WL-based methods decrease $\gamma_t$ far more rapidly,
which leads to more rapid convergence.  The Wang-Landau approaches can
get away with this because the range of energies of interest is given
as an input rather than an output, allowing a more aggressive schedule
of reduction of $\gamma_t$.  This aggressive behavior is precisely what
requires that Wang-Landau methods be followed by some correction stage
(either $1/t$ or a production run) in order to correct residual errors.
